Elders Moisture Summary

### 2020-06-09 stove_usage_cleaning.Rmd
update file paths

# Load, format, and save stove grades data
```{r}
## Box location: Update Box location once final data loaded
np_stove_initial <- read_xlsx("Input/NP/np_stove_20200225.xlsx") %>% 
  # rename variables
  mutate(home_id = as.factor(HomeID),
         home_winter_id = as.factor(HomeWinterID),
         stove_grade = as.factor(Score1),
         area = "NP") %>% 
  select(home_id, home_winter_id, area, stove_grade) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

## Box location: Update Box location once final data loaded
nn_stove_initial <- read_xlsx("Input/NN/nn_stove_20200225.xlsx") %>% 
  # rename variables
  mutate(home_id = as.factor(HomeID),
         home_winter_id = as.factor(HomeWinterID),
         stove_grade = as.factor(Score1),
         area = "NN") %>% 
  select(home_id, home_winter_id, area, stove_grade) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

#write_rds(elders_stove_grades, "Output/elders_stove_grades.rds")
```

# Clean up all stove grades data
```{r}
elders_stove_grades <- read_rds("Output/elders_stove_grades.rds")

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")

@@

# write_rds(elders_stove_grades_clean, "Output/elders_stove_grades_clean.rds")

elders_stove_grades_clean <- read_rds("Output/elders_stove_grades_clean.rds")
```

@@

# Load, format, and save stove usage data
```{r}
## Box location: Update Box location once final data loaded
np_stove_initial <- read_xlsx("Input/NP/np_woodstoveusage_20200225.xlsx") %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         burn_level = as.factor(Burning),
         wood_type = as.factor(Wood),
         wood_type_other = as.character(WhOtherWood),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  select(home_winter_id, area, sampling_visit, burn_level, wood_type, wood_type_other) %>% 
  arrange(home_winter_id, sampling_visit)

## Box location: Update Box location once final data loaded
nn_stove_initial <- read_xlsx("Input/NN/nn_woodstoveusage_20200225.xlsx") %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         burn_level = as.factor(Burning),
         wood_type = as.factor(Wood),
         wood_type_other = as.character(WhOtherWood),
         sampling_visit = as.factor(SamplingVisit),
         area = "NN") %>% 
  select(home_winter_id, area, sampling_visit, burn_level, wood_type, wood_type_other) %>% 
  arrange(home_winter_id, sampling_visit)

@@

#write_rds(elders_stove_usage, "Output/elders_stove_usage.rds")
```

# Clean up all stove usage data
```{r}
elders_stove_usage <- read_rds("Output/elders_stove_usage.rds")

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")

@@

# write_rds(elders_stove_usage_clean, "Output/elders_stove_usage_clean.rds")

elders_stove_usage_clean <- read_rds("Output/elders_stove_usage_clean.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")
```

# Load, format, and save stove grades data
```{r}
## Box location: Update Box location once final data loaded
np_stove_initial <- read_xlsx(paste0(file_path, "Input/NP/np_stove_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_id = as.factor(HomeID),
         home_winter_id = as.factor(HomeWinterID),
         stove_grade = as.factor(Score1),
         area = "NP") %>% 
  select(home_id, home_winter_id, area, stove_grade) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

## Box location: Update Box location once final data loaded
nn_stove_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_stove_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_id = as.factor(HomeID),
         home_winter_id = as.factor(HomeWinterID),
         stove_grade = as.factor(Score1),
         area = "NN") %>% 
  select(home_id, home_winter_id, area, stove_grade) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

#write_rds(elders_stove_grades, paste0(file_path, "Output/elders_stove_grades.rds"))
```

# Clean up all stove grades data
```{r}
elders_stove_grades <- read_rds(paste0(file_path, "Output/elders_stove_grades.rds"))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))

@@

# write_rds(elders_stove_grades_clean, paste0(file_path, "Output/elders_stove_grades_clean.rds"))

elders_stove_grades_clean <- read_rds(paste0(file_path, "Output/elders_stove_grades_clean.rds"))
```

@@

# Load, format, and save stove usage data
```{r}
## Box location: Update Box location once final data loaded
np_stove_initial <- read_xlsx(paste0(file_path, "Input/NP/np_woodstoveusage_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         burn_level = as.factor(Burning),
         wood_type = as.factor(Wood),
         wood_type_other = as.character(WhOtherWood),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  select(home_winter_id, area, sampling_visit, burn_level, wood_type, wood_type_other) %>% 
  arrange(home_winter_id, sampling_visit)

## Box location: Update Box location once final data loaded
nn_stove_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_woodstoveusage_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         burn_level = as.factor(Burning),
         wood_type = as.factor(Wood),
         wood_type_other = as.character(WhOtherWood),
         sampling_visit = as.factor(SamplingVisit),
         area = "NN") %>% 
  select(home_winter_id, area, sampling_visit, burn_level, wood_type, wood_type_other) %>% 
  arrange(home_winter_id, sampling_visit)

@@

#write_rds(elders_stove_usage, paste0(file_path, "Output/elders_stove_usage.rds"))
```

# Clean up all stove usage data
```{r}
elders_stove_usage <- read_rds(paste0(file_path, "Output/elders_stove_usage.rds"))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))

@@

# write_rds(elders_stove_usage_clean, paste0(file_path, "Output/elders_stove_usage_clean.rds"))

elders_stove_usage_clean <- read_rds(paste0(file_path, "Output/elders_stove_usage_clean.rds"))
```

### 2020-06-09 wood_moisture_cleaning.Rmd
update file paths

# Load, format, and save wood moisture data
```{r}
## Box location: Update Box location once final data loaded
np_moisture_initial <- read_xlsx("Input/NP/np_moisture_20200225.xlsx") %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         moisture_date = ymd(CompletedDate),
         moisture_1 = as.numeric(Moisture1),
         moisture_2 = as.numeric(Moisture2),
         moisture_3 = as.numeric(Moisture3),
         moisture_ave = as.numeric(MoistureAve),
         moisture_split = as.factor(Split),
         area = "NP") %>% 
  # replace 0 and -999 values with NA
  replace_with_na(replace = list(moisture_1 = 0, moisture_2 = 0,
                                 moisture_3 = 0, moisture_ave = 0)) %>% 
  replace_with_na(replace = list(moisture_1 = -999, moisture_2 = -999,
                                 moisture_3 = -999)) %>% 
  # gather 3 moisture samples to calculate average
  gather("sample", "value", c("moisture_1":"moisture_3")) %>% 
  arrange(home_winter_id, moisture_date) %>% 
  group_by(home_winter_id, moisture_date) %>% 
  mutate(moisture_ave = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>% 
  select(home_winter_id, area, moisture_date, 
         moisture_1, moisture_2, moisture_3, 
         moisture_ave, moisture_split) %>% 
  replace_with_na(replace = list(moisture_ave = "NaN")) %>%
  filter(!is.na(moisture_ave)) %>% 
  arrange(home_winter_id, moisture_date)

## Box location: Update Box location once final data loaded
nn_moisture_initial <- read_xlsx("Input/NN/nn_moisture_20200225.xlsx") %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         moisture_date = ymd(CompletedDate),
         moisture_1 = as.numeric(Moisture1),
         moisture_2 = as.numeric(Moisture2),
         moisture_3 = as.numeric(Moisture3),
         moisture_ave = as.numeric(MoistureAve),
         moisture_split = as.factor(Split),
         area = "NN") %>% 
  # replace 0 and -999 values with NA
  replace_with_na(replace = list(moisture_1 = 0, moisture_2 = 0,
                                 moisture_3 = 0, moisture_ave = 0)) %>% 
  replace_with_na(replace = list(moisture_1 = -999, moisture_2 = -999,
                                 moisture_3 = -999)) %>% 
  # gather 3 moisture samples to calculate average
  gather("sample", "value", c("moisture_1":"moisture_3")) %>% 
  arrange(home_winter_id, moisture_date) %>% 
  group_by(home_winter_id, moisture_date) %>% 
  mutate(moisture_ave = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>% 
  select(home_winter_id, area, moisture_date, 
         moisture_1, moisture_2, moisture_3, 
         moisture_ave, moisture_split) %>% 
  replace_with_na(replace = list(moisture_ave = "NaN")) %>%
  filter(!is.na(moisture_ave)) %>% 
  arrange(home_winter_id, moisture_date)

@@

#write_rds(elders_moisture, "Output/elders_moisture.rds")
```

# Clean up all moisture data
```{r}
elders_moisture <- read_rds("Output/elders_moisture.rds")

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")

@@

# write_rds(elders_moisture_clean, "Output/elders_moisture_clean.rds")

elders_moisture_clean <- read_rds("Output/elders_moisture_clean.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")
```

# Load, format, and save wood moisture data
```{r}
## Box location: Update Box location once final data loaded
np_moisture_initial <- read_xlsx(paste0(file_path, "Input/NP/np_moisture_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         moisture_date = ymd(CompletedDate),
         moisture_1 = as.numeric(Moisture1),
         moisture_2 = as.numeric(Moisture2),
         moisture_3 = as.numeric(Moisture3),
         moisture_ave = as.numeric(MoistureAve),
         moisture_split = as.factor(Split),
         area = "NP") %>% 
  # replace 0 and -999 values with NA
  replace_with_na(replace = list(moisture_1 = 0, moisture_2 = 0,
                                 moisture_3 = 0, moisture_ave = 0)) %>% 
  replace_with_na(replace = list(moisture_1 = -999, moisture_2 = -999,
                                 moisture_3 = -999)) %>% 
  # gather 3 moisture samples to calculate average
  gather("sample", "value", c("moisture_1":"moisture_3")) %>% 
  arrange(home_winter_id, moisture_date) %>% 
  group_by(home_winter_id, moisture_date) %>% 
  mutate(moisture_ave = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>% 
  select(home_winter_id, area, moisture_date, 
         moisture_1, moisture_2, moisture_3, 
         moisture_ave, moisture_split) %>% 
  replace_with_na(replace = list(moisture_ave = "NaN")) %>%
  filter(!is.na(moisture_ave)) %>% 
  arrange(home_winter_id, moisture_date)

## Box location: Update Box location once final data loaded
nn_moisture_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_moisture_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         moisture_date = ymd(CompletedDate),
         moisture_1 = as.numeric(Moisture1),
         moisture_2 = as.numeric(Moisture2),
         moisture_3 = as.numeric(Moisture3),
         moisture_ave = as.numeric(MoistureAve),
         moisture_split = as.factor(Split),
         area = "NN") %>% 
  # replace 0 and -999 values with NA
  replace_with_na(replace = list(moisture_1 = 0, moisture_2 = 0,
                                 moisture_3 = 0, moisture_ave = 0)) %>% 
  replace_with_na(replace = list(moisture_1 = -999, moisture_2 = -999,
                                 moisture_3 = -999)) %>% 
  # gather 3 moisture samples to calculate average
  gather("sample", "value", c("moisture_1":"moisture_3")) %>% 
  arrange(home_winter_id, moisture_date) %>% 
  group_by(home_winter_id, moisture_date) %>% 
  mutate(moisture_ave = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>% 
  select(home_winter_id, area, moisture_date, 
         moisture_1, moisture_2, moisture_3, 
         moisture_ave, moisture_split) %>% 
  replace_with_na(replace = list(moisture_ave = "NaN")) %>%
  filter(!is.na(moisture_ave)) %>% 
  arrange(home_winter_id, moisture_date)

@@

#write_rds(elders_moisture, paste0(file_path, "Output/elders_moisture.rds"))
```

# Clean up all moisture data
```{r}
elders_moisture <- read_rds(paste0(file_path, "Output/elders_moisture.rds"))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))

@@

# write_rds(elders_moisture_clean, paste0(file_path, "Output/elders_moisture_clean.rds"))

elders_moisture_clean <- read_rds(paste0(file_path, "Output/elders_moisture_clean.rds"))
```

### 2020-06-09 wood_moisture_summary.Rmd
update file paths

```{r}
# Load data
moisture_clean <- read_rds("Output/elders_moisture_clean.rds")
elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")
elders_pm <- read_rds("Output/elders_pm_clean.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

# Load data
moisture_clean <- read_rds(paste0(file_path, "Output/elders_moisture_clean.rds"))
elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))
elders_pm <- read_rds(paste0(file_path, "Output/elders_pm_clean.rds"))
```
